Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-10 paper_comparison/paper_comparison/paper_comparison.Rmd
revise the p-value part

Depending on the natural logarithm of the effect, lineups are classified into three categories: easy (< 1.5), moderate (1.5 - 3.5) and difficult (> 3.5). Figure \ref{fig:p-value-comparison} provides a mosaic plot showing the rejection rate of visual tests and conventional tests at different difficulty levels.

@@

For easy lineups produced by the non-linearity model, 65% are rejected by both the conventional and visual tests, while 9% are accepted by both tests. Thus, 74% of the time two tests will agree with each other. There are 16% of lineups rejected only by the conventional test.

Interestingly, in spite of the greater power of the conventional test, 10% of the lineups are rejected only by the visual test. This means among those accepted by the conventional test, 51% are rejected by the visual test. Recall that the RESET test used in our analysis includes powers of fitted values up to four. However, the "M" and "Triple-U" shapes constructed from the Hermite polynomials contain powers of regressor up to six and 18 respectively. In fact, by including the powers of fitted values up to six, all cases will be rejected by the RESET test. And from the example plot displayed in Figure \ref{fig:easy-poly-example}, we can observe panel three is distinctly different from others exhibiting a "M" shape. It clearly suggests users of the RESET test and any other residual-based conventional tests that require the specification of variables of interest to check the residual plot before conducting the test, such that the correct choice of variables can be made.

```{r easy-poly-example, fig.height = 5, fig.cap = "An example easy lineup produced by the non-linearity model not rejected by the conventional test but rejected by the visual test. Panel three exhibits strong non-linear pattern."}
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r easy-heter-example1, fig.height = 5, fig.cap = "An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 17 exhibits strong heteroskedasticity pattern."}
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r easy-heter-example2, fig.height = 5, fig.cap = "An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 18 contains a distinct outlier."}
VI_MODEL$plot_lineup(vi_lineup$heter_536$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

For easy lineups produced by the heteroskedasticity model, 62% are rejected by both the conventional test and the visual test, and 7% are accepted by both, result in 69% agreement rate. Lineups rejected by only conventional test are 30%. 1% of lineups are accepted by the conventional test but rejected by the visual test.

Among those 1% lineups, which are two lineups, one shows detectable heteroskedasticity pattern as displayed in Figure \ref{fig:easy-heter-example1}. Another contain data plot with an noticeable outlier, but the "Right-triangle" shape is not obvious as shown in Figure \ref{fig:easy-heter-example2}. The $p$-values of Breusch-Pagan test for these two lineups are $0.055$ and $0.135$. Compared to the visual test, its $p$-values are $0.026$ and $0.012$. The Breusch-Pagan test should reject the one with obvious heteroskedasticity signal, but it yields a $p$-value slightly above 5%.

@@

With the increase of the difficulty level, the sensitivity of conventional tests enlarge the difference in rejection rates. For moderate lineup produced by the non-linearity model, only 8% and 28% are rejected and accepted by both respectively. We can observe a decline in agreement rate to 36%. A huge amount of lineups are accepted by the visual test. 63% of lineups rejected only by the conventional test. There are 1% of lineups which rejected only by conventional tests suffer the same RESET test issue as mentioned earlier.

For those produced by the heteroskedasticy model, the corresponding numbers are 23%, 31%, 54%, 45% and 1%. Only one lineup rejected by the visual test but accepted by the conventional test. It shows zero heteroskedasticity patterns, but contains a few outliers at the bottom of the data plot as illustrated in panel 14 of Figure \ref{fig:moderate-heter-example1}. Two out of five subjects correctly identify this lineup yielding a $p$-value equal to $0.044$.

```{r moderate-heter-example1, fig.height = 5, fig.cap = "An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 14 contains a few outliers at the bottom of the panel."}
VI_MODEL$plot_lineup(vi_lineup$heter_219$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

Visual test is insensitive to lineups with small effect. When it comes to difficult lineups produced by the non-linearity model, none of them are rejected by the visual test. There are 73% of lineups accepted by both tests, and 26% rejected by the conventional test. The agreement rate rise up to 73%.

For lineups produced by the heteroskedasticity model, 3% are rejected by both, 71% are accepted by both, 24% are rejected only by the conventional test and 2% are rejected only by the visual test, which are two lineups.

As shown in \ref{fig:difficult-heter-example1} and \ref{fig:difficult-heter-example2}, residual plots of both lineups are constructed with $X_{raw} \sim lognormal(0, 0.6^2)/3$. Though the designed patterns are "Left-triangle" and "Butterfly", both of them are invisible due to the small effect. The residual plots are dominated by the skewed distribution. Further, no distinguishable visual patterns, such as outliers, are detectable from the data plot of these two lineups, which are panel 5 and panel 15. The data plot in these two lineups are not the most different plot from our point of view either. However, three out of five and two out of five subjects correctly identify the data plot for these two lineups respectively. But the reasons for selecting the plot provided by the subjects are not consistent. Therefore, with the current data, we can not explain why subjects can correctly identify the data plot of these two lineups. Collecting more data in future study may help to answer this question.

```{r difficult-heter-example1, fig.height = 5, fig.cap = "An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 14 contains a few outliers at the bottom of the panel."}
VI_MODEL$plot_lineup(vi_lineup$heter_224$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r difficult-heter-example2, fig.height = 5, fig.cap = "An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 14 contains a few outliers at the bottom of the panel."}
VI_MODEL$plot_lineup(vi_lineup$heter_415$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

>>>>

Depending on the natural logarithm of the effect, lineups are classified into three categories: easy (> 3.5), moderate (1.5 - 3.5) and difficult (< 1.5). Figure \ref{fig:p-value-comparison} provides a mosaic plot showing the rejection rate of visual tests and conventional tests at different difficulty levels.

@@

For easy lineups produced by the non-linearity model, 65% are rejected by both the conventional and visual tests, while 9% are accepted by both tests. Thus, 74% of the time two tests will agree with each other. There are 16% of lineups rejected by the conventional test only.

Interestingly, in spite of the greater power of the conventional test, 10% of the lineups are rejected by the visual test only. Recall that the RESET test used in our analysis includes powers of fitted values up to four. However, the "M" and the "Triple-U" shapes constructed from the Hermite polynomials contain powers of the regressor up to six and 18 respectively. In fact, by including the powers of fitted values up to six in the RESET test, all cases will be rejected. We also can observe from the example plot displayed in Figure \ref{fig:easy-poly-example} that panel three is distinctly different from others, exhibiting a "M" shape. This clearly suggests users of the RESET test and any other residual-based conventional tests that require the specification of variables of interest to check the residual plot before conducting the test, such that the correct choice of variables can be made.

```{r easy-poly-example, fig.height = 5, fig.cap = "Lineup poly-270 produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern."}
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

For easy lineups produced by the heteroskedasticity model, 62% are rejected by both the conventional test and the visual test, and 7% are accepted by both, result in 69% agreement rate. Lineups only rejected by conventional test are 30%. 1% of lineups are accepted by the conventional test but rejected by the visual test.

Among those 1%, which are two lineups, one shows detectable heteroskedasticity pattern as displayed in Figure \ref{fig:easy-heter-example1}. Another contain data plot with an noticeable outlier, but the "Right-triangle" shape is not very strong as shown in Figure \ref{fig:easy-heter-example2}. The $p$-values of Breusch-Pagan test for these two lineups are $0.055$ and $0.135$. Compared to the visual test, its $p$-values are $0.026$ and $0.012$. The Breusch-Pagan test should reject the one with obvious heteroskedasticity signal, but it yields a $p$-value slightly above 5%.

```{r easy-heter-example1, fig.height = 5, fig.cap = 'Lineup heter-331 produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.'}
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r easy-heter-example2, fig.height = 5, fig.cap = "Lineup heter-536 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 18 exhibits a vague heteroskedasticity pattern, but it contains a distinct outlier which makes it attractive to subjects."}
VI_MODEL$plot_lineup(vi_lineup$heter_536$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

With the increase of the difficulty level, the sensitivity of conventional tests enlarge the difference in rejection rates. For moderate lineup produced by the non-linearity model, 8% and 28% are rejected and accepted by both tests respectively. We can observe a decline in agreement rate to 36%. A large proportion of lineups are accepted by the visual test and rejected by the conventional test, which is around 63%. The remaining 1% are rejected by conventional tests only, which suffer the same issue caused by the RESET test as mentioned earlier.

For those produced by the heteroskedasticy model, the corresponding numbers are 23%, 31%, 54%, 45% and 1%. There is only one lineup rejected by the visual test but accepted by the conventional test. It does not show any heteroskedasticity patterns, but contains a few outliers at the bottom of the data plot as illustrated in panel 14 of Figure \ref{fig:moderate-heter-example1}. Two out of five subjects correctly identify this lineup yielding a $p$-value equal to $0.044$. We consider this instance is rejected by chance. If a different set of null plots are used, the data plot may not be identified.

```{r moderate-heter-example1, fig.height = 5, fig.cap = "Lineup heter-219 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Though the data plot at panel 14 shows no heteroskedasticity patterns, it contains a few outliers at the bottom of the panel."}
VI_MODEL$plot_lineup(vi_lineup$heter_219$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

Visual test is insensitive to lineups with small effect. When it comes to difficult level, none of the lineups produced by the non-linearity model are rejected by the visual test. There are 73% of lineups accepted by both tests, and 26% rejected by the conventional test. The agreement rate rise up to 73%.

For lineups produced by the heteroskedasticity model, 3% are rejected by both tests, and 71% are accepted by both tests. There are 24% of lineups rejected by the conventional test only. Besides, only two lineups, which is 2% of all the difficult lineups, are rejected by the visual test only.

As shown in \ref{fig:difficult-heter-example1} and \ref{fig:difficult-heter-example2}, residual plots of both lineups are constructed with $X_{raw} \sim lognormal(0, 0.6^2)/3$. Though the designed patterns are "Left-triangle" and "Butterfly" shape, both of them are invisible due to the small effect. The visual effect are dominated by the skewed distribution. Further, no distinguishable visual patterns, such as outliers, are detectable from the data plot of these two lineups, which are panel 5 and panel 15. The data plots in these two lineups are not the most different plot from our point of view either. However, three out of five and two out of five subjects correctly identify the data plot for these two lineups respectively. But the reasons for selecting the plot provided by the subjects are mixed and inconsistent. Hence, with the current data, we can not explain why subjects can correctly identify the data plot of these two lineups. Collecting more data in future study may help to answer this question.

```{r difficult-heter-example1, fig.height = 5, fig.cap = "Lineup heter-224 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Although two out of five subjects correctly identify the data plot at panel 5, it does not exhibit any visually distinguishable pattern."}
VI_MODEL$plot_lineup(vi_lineup$heter_224$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r difficult-heter-example2, fig.height = 5, fig.cap = "Lineup heter-415 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Panel 15 is the data plot but it does not exhibit any visually distinguishable pattern."}
VI_MODEL$plot_lineup(vi_lineup$heter_415$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

### 2023-01-10 paper_comparison/paper_comparison/paper_comparison.tex
revise the p-value part

Depending on the natural logarithm of the effect, lineups are classified
into three categories: easy (\textless{} 1.5), moderate (1.5 - 3.5) and
difficult (\textgreater{} 3.5). Figure \ref{fig:p-value-comparison}
provides a mosaic plot showing the rejection rate of visual tests and
conventional tests at different difficulty levels.

@@

For easy lineups produced by the non-linearity model, 65\% are rejected
by both the conventional and visual tests, while 9\% are accepted by
both tests. Thus, 74\% of the time two tests will agree with each other.
There are 16\% of lineups rejected only by the conventional test.

Interestingly, in spite of the greater power of the conventional test,
10\% of the lineups are rejected only by the visual test. This means
among those accepted by the conventional test, 51\% are rejected by the
visual test. Recall that the RESET test used in our analysis includes
powers of fitted values up to four. However, the ``M'' and ``Triple-U''
shapes constructed from the Hermite polynomials contain powers of
regressor up to six and 18 respectively. In fact, by including the
powers of fitted values up to six, all cases will be rejected by the
RESET test. And from the example plot displayed in Figure
\ref{fig:easy-poly-example}, we can observe panel three is distinctly
different from others exhibiting a ``M'' shape. It clearly suggests
users of the RESET test and any other residual-based conventional tests
that require the specification of variables of interest to check the
residual plot before conducting the test, such that the correct choice
of variables can be made.

@@

\caption{An example easy lineup produced by the non-linearity model not rejected by the conventional test but rejected by the visual test. Panel three exhibits strong non-linear pattern.}\label{fig:easy-poly-example}
\end{figure}

@@

\caption{An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 17 exhibits strong heteroskedasticity pattern.}\label{fig:easy-heter-example1}
\end{figure}

@@

\caption{An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 18 contains a distinct outlier.}\label{fig:easy-heter-example2}
\end{figure}

For easy lineups produced by the heteroskedasticity model, 62\% are
rejected by both the conventional test and the visual test, and 7\% are
accepted by both, result in 69\% agreement rate. Lineups rejected by
only conventional test are 30\%. 1\% of lineups are accepted by the
conventional test but rejected by the visual test.

Among those 1\% lineups, which are two lineups, one shows detectable
heteroskedasticity pattern as displayed in Figure
\ref{fig:easy-heter-example1}. Another contain data plot with an
noticeable outlier, but the ``Right-triangle'' shape is not obvious as
shown in Figure \ref{fig:easy-heter-example2}. The \(p\)-values of
Breusch-Pagan test for these two lineups are \(0.055\) and \(0.135\).
Compared to the visual test, its \(p\)-values are \(0.026\) and
\(0.012\). The Breusch-Pagan test should reject the one with obvious
heteroskedasticity signal, but it yields a \(p\)-value slightly above
5\%.

@@

With the increase of the difficulty level, the sensitivity of
conventional tests enlarge the difference in rejection rates. For
moderate lineup produced by the non-linearity model, only 8\% and 28\%
are rejected and accepted by both respectively. We can observe a decline
in agreement rate to 36\%. A huge amount of lineups are accepted by the
visual test. 63\% of lineups rejected only by the conventional test.
There are 1\% of lineups which rejected only by conventional tests
suffer the same RESET test issue as mentioned earlier.

For those produced by the heteroskedasticy model, the corresponding
numbers are 23\%, 31\%, 54\%, 45\% and 1\%. Only one lineup rejected by
the visual test but accepted by the conventional test. It shows zero
heteroskedasticity patterns, but contains a few outliers at the bottom
of the data plot as illustrated in panel 14 of Figure
\ref{fig:moderate-heter-example1}. Two out of five subjects correctly
identify this lineup yielding a \(p\)-value equal to \(0.044\).

@@

\caption{An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 14 contains a few outliers at the bottom of the panel.}\label{fig:moderate-heter-example1}
\end{figure}

@@

Visual test is insensitive to lineups with small effect. When it comes
to difficult lineups produced by the non-linearity model, none of them
are rejected by the visual test. There are 73\% of lineups accepted by
both tests, and 26\% rejected by the conventional test. The agreement
rate rise up to 73\%.

For lineups produced by the heteroskedasticity model, 3\% are rejected
by both, 71\% are accepted by both, 24\% are rejected only by the
conventional test and 2\% are rejected only by the visual test, which
are two lineups.

As shown in \ref{fig:difficult-heter-example1} and
\ref{fig:difficult-heter-example2}, residual plots of both lineups are
constructed with \(X_{raw} \sim lognormal(0, 0.6^2)/3\). Though the
designed patterns are ``Left-triangle'' and ``Butterfly'', both of them
are invisible due to the small effect. The residual plots are dominated
by the skewed distribution. Further, no distinguishable visual patterns,
such as outliers, are detectable from the data plot of these two
lineups, which are panel 5 and panel 15. The data plot in these two
lineups are not the most different plot from our point of view either.
However, three out of five and two out of five subjects correctly
identify the data plot for these two lineups respectively. But the
reasons for selecting the plot provided by the subjects are not
consistent. Therefore, with the current data, we can not explain why
subjects can correctly identify the data plot of these two lineups.
Collecting more data in future study may help to answer this question.

@@

\caption{An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 14 contains a few outliers at the bottom of the panel.}\label{fig:difficult-heter-example1}
\end{figure}

@@

\caption{An example easy lineup produced by the heteroskedasticity not rejected by the conventional test but rejected by the visual test. Panel 14 contains a few outliers at the bottom of the panel.}\label{fig:difficult-heter-example2}
\end{figure}

>>>>

Depending on the natural logarithm of the effect, lineups are classified
into three categories: easy (\textgreater{} 3.5), moderate (1.5 - 3.5)
and difficult (\textless{} 1.5). Figure \ref{fig:p-value-comparison}
provides a mosaic plot showing the rejection rate of visual tests and
conventional tests at different difficulty levels.

@@

For easy lineups produced by the non-linearity model, 65\% are rejected
by both the conventional and visual tests, while 9\% are accepted by
both tests. Thus, 74\% of the time two tests will agree with each other.
There are 16\% of lineups rejected by the conventional test only.

Interestingly, in spite of the greater power of the conventional test,
10\% of the lineups are rejected by the visual test only. Recall that
the RESET test used in our analysis includes powers of fitted values up
to four. However, the ``M'' and the ``Triple-U'' shapes constructed from
the Hermite polynomials contain powers of the regressor up to six and 18
respectively. In fact, by including the powers of fitted values up to
six in the RESET test, all cases will be rejected. We also can observe
from the example plot displayed in Figure \ref{fig:easy-poly-example}
that panel three is distinctly different from others, exhibiting a ``M''
shape. This clearly suggests users of the RESET test and any other
residual-based conventional tests that require the specification of
variables of interest to check the residual plot before conducting the
test, such that the correct choice of variables can be made.

@@

\caption{Lineup poly-270 produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern.}\label{fig:easy-poly-example}
\end{figure}

For easy lineups produced by the heteroskedasticity model, 62\% are
rejected by both the conventional test and the visual test, and 7\% are
accepted by both, result in 69\% agreement rate. Lineups only rejected
by conventional test are 30\%. 1\% of lineups are accepted by the
conventional test but rejected by the visual test.

Among those 1\%, which are two lineups, one shows detectable
heteroskedasticity pattern as displayed in Figure
\ref{fig:easy-heter-example1}. Another contain data plot with an
noticeable outlier, but the ``Right-triangle'' shape is not very strong
as shown in Figure \ref{fig:easy-heter-example2}. The \(p\)-values of
Breusch-Pagan test for these two lineups are \(0.055\) and \(0.135\).
Compared to the visual test, its \(p\)-values are \(0.026\) and
\(0.012\). The Breusch-Pagan test should reject the one with obvious
heteroskedasticity signal, but it yields a \(p\)-value slightly above
5\%.

@@

\caption{Lineup heter-331 produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.}\label{fig:easy-heter-example1}
\end{figure}

@@

\caption{Lineup heter-536 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 18 exhibits a vague heteroskedasticity pattern, but it contains a distinct outlier which makes it attractive to subjects.}\label{fig:easy-heter-example2}
\end{figure}

@@

With the increase of the difficulty level, the sensitivity of
conventional tests enlarge the difference in rejection rates. For
moderate lineup produced by the non-linearity model, 8\% and 28\% are
rejected and accepted by both tests respectively. We can observe a
decline in agreement rate to 36\%. A large proportion of lineups are
accepted by the visual test and rejected by the conventional test, which
is around 63\%. The remaining 1\% are rejected by conventional tests
only, which suffer the same issue caused by the RESET test as mentioned
earlier.

For those produced by the heteroskedasticy model, the corresponding
numbers are 23\%, 31\%, 54\%, 45\% and 1\%. There is only one lineup
rejected by the visual test but accepted by the conventional test. It
does not show any heteroskedasticity patterns, but contains a few
outliers at the bottom of the data plot as illustrated in panel 14 of
Figure \ref{fig:moderate-heter-example1}. Two out of five subjects
correctly identify this lineup yielding a \(p\)-value equal to
\(0.044\). We consider this instance is rejected by chance. If a
different set of null plots are used, the data plot may not be
identified.

@@

\caption{Lineup heter-219 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Though the data plot at panel 14 shows no heteroskedasticity patterns, it contains a few outliers at the bottom of the panel.}\label{fig:moderate-heter-example1}
\end{figure}

@@

Visual test is insensitive to lineups with small effect. When it comes
to difficult level, none of the lineups produced by the non-linearity
model are rejected by the visual test. There are 73\% of lineups
accepted by both tests, and 26\% rejected by the conventional test. The
agreement rate rise up to 73\%.

For lineups produced by the heteroskedasticity model, 3\% are rejected
by both tests, and 71\% are accepted by both tests. There are 24\% of
lineups rejected by the conventional test only. Besides, only two
lineups, which is 2\% of all the difficult lineups, are rejected by the
visual test only.

As shown in \ref{fig:difficult-heter-example1} and
\ref{fig:difficult-heter-example2}, residual plots of both lineups are
constructed with \(X_{raw} \sim lognormal(0, 0.6^2)/3\). Though the
designed patterns are ``Left-triangle'' and ``Butterfly'' shape, both of
them are invisible due to the small effect. The visual effect are
dominated by the skewed distribution. Further, no distinguishable visual
patterns, such as outliers, are detectable from the data plot of these
two lineups, which are panel 5 and panel 15. The data plots in these two
lineups are not the most different plot from our point of view either.
However, three out of five and two out of five subjects correctly
identify the data plot for these two lineups respectively. But the
reasons for selecting the plot provided by the subjects are mixed and
inconsistent. Hence, with the current data, we can not explain why
subjects can correctly identify the data plot of these two lineups.
Collecting more data in future study may help to answer this question.

@@

\caption{Lineup heter-224 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Although two out of five subjects correctly identify the data plot at panel 5, it does not exhibit any visually distinguishable pattern.}\label{fig:difficult-heter-example1}
\end{figure}

@@

\caption{Lineup heter-415 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Panel 15 is the data plot but it does not exhibit any visually distinguishable pattern.}\label{fig:difficult-heter-example2}
\end{figure}
